Transfer Learning for Depression Detection on Social Networks\thanks{Supported by School of Information System, University of Southern Queensland, Australia}

### 2018-10-26 Paper/version 0/paper.tex
ensemble classifier

\textbf{Definition 1} \textit{Let $\mathbb{S}$ be a set of user properties to present an effective user profile for depression, a user property s $\in$ $\mathbb{S}$ is a tuple s := $\langle$ p{\tiny{1}}, p{\tiny{2}}, p{\tiny{3}}, $\cdots$ p{\tiny{n}} $\rangle$, where

@@

\textbf{Definition 3} \textit{Let $\mathbb{U}$ = $\langle$ u{\tiny{1}}, u{\tiny{2}}, u{\tiny{3}}, $\cdots$ u{\tiny{k}} $\rangle$ be a subset of $\mathbb{S}$, any element u $\in$ $\mathbb{U}$ is a tuple u := $\langle$ p'{\tiny{1}}, p'{\tiny{2}}, p'{\tiny{3}}, $\cdots$ p'{\tiny{n'}} $\rangle$,where

@@

This research aims to discover an effective classification model $\mathbb{M}$ which provides a reliable mapping of a well-defined $\mathbb{U}$ into $\mathbb{V}$: \\

@@

	$\mathbb{U}$ $\xRightarrow{\text{$\mathbb{M}$ } }$ $\mathbb{V}$  or  $\mathbb{M}$($\mathbb{U}$) = $\mathbb{V}$

@@

\textbf{Definition 4} \textit{ Let new redesigned $\mathbb{U}$ = $\langle$ u{\tiny{mental}}, u{\tiny{social}}, u{\tiny{role}}, u{\tiny{pain}}, u{\tiny{physical}}, u{\tiny{overall}} $\rangle$, every u  $\in$ $\mathbb{U}$ is an independent function of user, where

@@

  \item u{\tiny{mental}} presents mental function;
  \item u{\tiny{social}} presents social function;
  \item u{\tiny{role}} presents role function;
  \item u{\tiny{pain}} presents pain function;
  \item u{\tiny{physical}} presents physical function;
  \item u{\tiny{overall}} presents the overall function.

>>>>

\textbf{Definition 1} \textit{Let $\mathbb{S}$ be a set of user properties to present an effective user profile for depression, a user property s $\in$ $\mathbb{S}$ is a tuple $s := \langle p_{1}, p_{2}, p_{3}$, $\cdots p_{n} \rangle$, where

@@

\textbf{Definition 3} \textit{Let $\mathbb{U} = \langle u_{1}, u_{2}, u_{3}$, $\cdots u_{k} \rangle$ be a subset of $\mathbb{S}$, any element u $\in \mathbb{U}$ is a tuple $u := \langle p'_{1}, p'_{2}, p'_{3}$, $\cdots p'_{n'} \rangle$,where

@@

This research aims to discover an effective classification model $\mathbb{M}$ which provides a reliable mapping of a well-defined $\mathbb{U}$ into $\mathbb{V}$:} \\

@@

	$\mathbb{U}$ $\xRightarrow{\mathbb{M}}$ $\mathbb{V}$  or  $\mathbb{M}$($\mathbb{U}$) = $\mathbb{V}$

@@

\textbf{Definition 4} \textit{ Let new redesigned $\mathbb{U}$ = $\langle u_{mental}, u_{social}, u_{role}, u_{pain}, u_{physical}, u_{overall} \rangle$, every u  $\in \mathbb{U}$ is an independent function of user, where

@@

  \item $u_{mental}$ presents mental function;
  \item $u_{social}$ presents social function;
  \item $u_{role}$ presents role function;
  \item $u_{pain}$ presents pain function;
  \item $u_{physical}$ presents physical function;
  \item $u_{overall}$ presents the overall function.
